Automated Verification of Stand-alone Solar Photovoltaic Systems

### 2019-04-08 Tex/elsevier/trindade_ren_and_sust_rev1.tex
added comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Related to the ESBMC, it was tried two possibilities, with the solvers Boolector and with Z3. The incremental option, that uses less memory, can only be performed with the solver Z3. Using ESBMC with the solver Boolector created a out of memory situation in all the case studies. And this result was obtained in less than six minutes of execution, i.e., the 64 G bytes of RAM were consumed by the verification engine and the processes was killed. This resulted in a UNKNOWN return from the tool, as shown at the first column in~\ref{cases}. However, using the same version of the ESBMC but with the Z3 solver, the experimentation returned SAT or UNSAT to all the case studies. Related to the cases that use a 700 W PV system, the tool could not reach an error in all the four houses and the execution time took from 4m27s to 5m08s. However the 1,200 W PV system (house 5) failed (SAT) at the line 337 of the code, indicating that the system is \textit{incorrectly} sized; in particular, the counterexample provided by the verification engine indicated that the nominal current from the charge controller is less than the minimum current demanded by the PV system in order to work properly. This verification took less than 1s to be performed.

Concerning the CBMC tool, similar results were obtained, but with some slower time. The experimentation returned SAT or UNSAT to all the case studies. Related to the 700 W PV systems, the tool could not reach an error in all the four houses and the execution time took from 18m36s to 19m02s. However the 1,200 W PV system (house 5) failed (SAT) at the line 337 of the code; with the same counterexample presented by ESBMC. This verification took less than 1s to be performed as well.

Finally, the CPAchecker tool presented some different results. Even using two different configuration possibilities, as described in Section~\ref{sec:setup}, the verification engine presented a UNKNOWN result for all the 700W systems. This is because the time out set up was reached, i.e., after 4 hours of execution the tool was not possible to decide if the verification was SAT or UNSAT. However, when verifying the 1,200W PV system, the tool presented the same SAT message, indicating the same line (337) of the code.

>>>>

Related to ESBMC, we have tried two possibilities with the SMT solvers Boolector and with Z3. The incremental option, which uses less memory, can only be performed with Z3. Using ESBMC with Boolector led to an out of memory situation in all the case studies. This result was obtained in less than six minutes of execution, i.e., the 64 G bytes of RAM were consumed by the verification engine and the processes was killed. This resulted in a UNKNOWN returned from the tool, as shown in the first column in Table~\ref{cases}. However, using the same version of ESBMC but with Z3, the experimentation returned SAT or UNSAT to all the case studies. Related to the cases that use a 700 W PV system, the tool \textcolor{red}{which tool?} could not reach an error in all the four houses and the execution time took from 4m27s to 5m08s. However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code, thereby indicating that the system is \textit{incorrectly} sized; in particular, the counterexample provided by the verification engine indicated that the nominal current from the charge controller is less than the minimum current demanded by the PV system in order to work properly \textcolor{red}{What does work properly mean?}. This verification took less than 1s to be performed \textcolor{red}{why?}.

Concerning the CBMC tool, similar results were obtained, but with some slower time. The experimentation returned SAT or UNSAT to all the case studies. Related to the 700 W PV systems, the tool could not reach an error in all the four houses and the execution time took from 18m36s to 19m02s. However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code; with the same counterexample presented by ESBMC. This verification took less than 1s to be performed as well \textcolor{red}{why?}.

Finally, the CPAchecker tool presented some different results. Even using two different configuration possibilities, as described in Section~\ref{sec:setup}, the verification engine presented an UNKNOWN result for all the 700W systems. This is because the time out set up was reached, i.e., after 4 hours of execution the tool was unable to decide if the verification was SAT or UNSAT. However, when verifying the 1,200W PV system, the tool presented the same SAT message \textcolor{red}{what is a SAT message?}, thereby indicating the same line (337) of the code.
